PLAE enables quick and easy searching across one million ocular transcriptomes

### 2022-07-07 manuscript_00.Rmd
move diff data pulls to sep script

toc()
```

@@

```{r scEiaD_data_overview, fig.height = 18, fig.width = 10, echo = F, message = F, fig.cap=scEiaD_data_overview_cap}
tic()
num1 <- meta_filter %>% filter(Organ == 'Eye') %>% pull(Tissue) %>% unique() %>% length()
num2 <- meta_filter %>% filter(Organ != 'Eye') %>% pull(Tissue) %>% unique() %>% length()
num3 <- meta_filter %>% filter(Organ == 'Eye') %>% pull(CellType) %>% unique() %>% length()
scEiaD_data_overview_cap <- fig_cap(name = 'scEiaD_data_overview', caption = glue::glue("Distribution of tissues and cell types in scEiaD. A. tabulation of the number of cells present across {num1} ocular and {num2} non-ocular tissues, B. Number of studies for each ocular tissue. C. Number of cells present across {num3} curated ocular-derived cell types."))

@@

```{r web_resources, fig.height = 15, fig.width = 20, echo = F, message = F, fig.cap=web_resources_cap}
tic()
web_resources_cap <- tab_cap(name = 'web_resources', caption = 'Comparison of PLAE with other web resources that contain single cell ocular datasets, as of 2021-03-15.')

feature_table <- rbind(
  c('PLAE','Yes','Yes', 'Yes', '1136 ', 'https://plae.nei.nih.gov'),
  c('Spectacle', 'Yes' ,'No', 'No', '1800', 'https://singlecell-eye.org'),
  c('UCSC Cell Browser', 'Yes', 'No', 'Yes', '62', 'https://cells.ucsc.edu' ),
  c('Tabula Sapiens', 'No', 'N/A', 'Yes', '10', 'https://tabula-sapiens-portal.ds.czbiohub.org'),
  c('PanglaoDB', 'Yes', 'No', 'Yes', '47', 'https://panglaodb.se'),
  c('Protein Atlas', 'Yes*','No', 'Yes', '5',  'https://www.proteinatlas.org/humanproteome/celltype')) %>% 
  as_tibble()
colnames(feature_table) <- c('Resource Name', 'Independent Datasets', 'Harmonization', 'Ocular and non-Ocular Data', 'Ocular Cell Count\n(thousands)', 'URL')
feature_table %>% flextable()
# as of 2021 10 25
toc()
```

@@

```{r}
tic()
# number of celltype (predict) - organism - study counts (with >=50 cells)
# ws == Well Supported
ws_table <- meta_filter %>%  
  filter(Organ == 'Eye') %>% 
  group_by(organism, CellType_predict, study_accession) %>% 
  count() %>% 
  filter(n >= 50) %>% 
  ungroup() %>% 
  group_by(organism, CellType_predict) %>% 
  count() %>% 
  pivot_wider(values_from = n, names_from = organism) %>% 
  filter(!is.na(CellType_predict)) %>% 
  replace(is.na(.), values = 0) %>% 
  arrange(CellType_predict) %>% 
  rename(`CellType (Predict)` = CellType_predict) %>% 
  mutate(`Well Supported` = case_when(`Homo sapiens` >= 2 & `Mus musculus` >= 2 ~ 'Yes',
                                      TRUE ~ 'No'))

# fix  occasional NA
# data made from src/ensdb.R
diff_tab_big <- read_tsv('data/diff_tab_big.tsv.gz')
down_tab_big <- read_tsv('data/down_tab_big.tsv.gz')
gene_tab <- bind_rows(read_tsv('data/hs.ensdb.v86.symbol.geneid.tsv.gz'), read_tsv('data/mm.ensdb.v79.symbol.geneid.tsv.gz'))
diff_tab <- diff_tab_big %>% 
  filter(Against == 'All', 
         Base %in% (meta_filter %>% filter(Organ == 'Eye') %>% 
                      pull(CellType) %>% unique()))

diff_tab_sup <- diff_tab %>% 
  group_by(Base, Organism) %>% 
  summarise(Count = n()) %>% 
  rename(`CellType (Predict)` = Base, `Differentially Expressed Gene Count` = Count) %>% 
  pivot_wider(values_from = `Differentially Expressed Gene Count`, names_from = Organism) %>% replace(is.na(.),0) %>% 
  as_tibble()

diff_tab_sup <- bind_rows(
  diff_tab_sup,
  ws_table$`CellType (Predict)`[!ws_table$`CellType (Predict)` %in% 
                                  diff_tab_sup$`CellType (Predict)`] %>% 
    enframe() %>% 
    select(`CellType (Predict)` = value) %>%
    mutate(`Homo sapiens` = 0, `Mus musculus` = 0, `Macaca fascicularis` = 0) %>% 
    arrange(`CellType (Predict)`)
)

write_csv(diff_tab, file = 'supplemental_files/differential_expression_table.csv.gz')

@@

toc()
```

@@

```{r}
tic()
ws_oct <- ws_table %>% filter(`Well Supported` == 'Yes') %>% pull(`CellType (Predict)`)

consist_diff <- scEiaD_2020_v01 %>% 
  tbl("diff_testing") %>% 
  filter(Base %in% ws_oct) %>%  
  filter(Group == 'CellType (Predict)', 
         Against == 'All') %>% 
  group_by(Base, Gene) %>% 
  summarise(`mean log2FC` = mean(log2FoldChange), `sig count` = sum(padj < 1e-4), `mean padj` = mean(padj)) %>% 
  filter(`mean log2FC` > 2, `sig count` > 1, `mean padj` < 1e-5) %>%  
  collect() %>% 
  mutate(GENEID = str_extract(Gene, 'ENS\\w+')) %>% 
  left_join(gene_tab, by = 'GENEID') %>% 
  relocate(SYMBOL, GENEID) %>% 
  dplyr::rename(Symbol = SYMBOL, ID = GENEID) %>% 
  arrange(-`mean log2FC`)

# id diff genes only seen once across the cell types
uniq_g <- consist_diff %>% group_by(Symbol) %>% count() %>% filter(n == 1)
consist_diff %>% group_by(Base) %>% summarise(Count = n())
consist_diff %>% filter(Symbol %in% uniq_g$Symbol) %>% group_by(Base) %>% summarise(Count = n())

consist_diff %>% filter(Symbol %in% uniq_g$Symbol) %>% group_by(Base) %>% summarise(Count = n()) %>% ggplot(aes(x=`Base`, y = `Count` )) + geom_bar(stat='identity', position = 'dodge') + cowplot::theme_cowplot() + coord_flip() + xlab("CellTye (Predict)")
toc()
```

```{r, fig.height=11, fig.width=6}
tic()
g <- consist_diff %>% filter(Symbol %in% uniq_g$Symbol) %>% group_by(Base) %>% slice_max(n=8, order_by = `mean log2FC`) %>% mutate(g = paste0(Symbol, ' (', ID, ')')) %>% pull(g)

test <- scEiaD_2020_v01 %>%
  tbl("diff_testing") %>%
  filter(Gene %in% g) %>%
  collect() %>%
  filter(Base %in% ws_oct,
         Group == 'CellType (Predict)',
         Against == 'All') %>%
  select(Gene, Organism, log2FoldChange, Base)

x <- test %>% 
  mutate(GO = paste0(Base, '_', Organism)) %>% 
  select(-Organism, -Base) %>% 
  pivot_wider(values_from=log2FoldChange, names_from = GO)
celltype <- colnames(x[,-1])
x <- x %>% data.frame()
row.names(x) <- x$Gene

x <- x[,-1]

organism <- str_extract(celltype, '_\\w+ \\w+') %>% gsub('_','',.)
cts  <- str_extract(celltype, '.*_') %>% gsub('_','',.)
genes <- row.names(x) %>% gsub(' \\(.*','',.)

base_yo <- genes %>% as_tibble() %>% rename(Symbol = value) %>% left_join(consist_diff %>% select(Symbol, Base) %>% unique()) %>% pull(Base)

hm <- ComplexHeatmap::Heatmap(x, column_labels = organism, 
                              column_split = cts, 
                              row_split = base_yo, show_row_dend = FALSE, 
                              row_labels = genes, 
                              column_title_rot = 90, 
                              name = 'log2FC', use_raster = TRUE,
                              row_title_rot = 0)
ComplexHeatmap::draw(hm, padding = unit(c(2, 2, 32, 2), "mm"), row_title = "Marker Genes")
toc()
```

@@

Neurogenic and RPC have very similar expression patterns. We leverage our more specific differential test to directly assess genes were are different between neurogenic cells and RPC. We show the top 5 genes that are both more highly expressed in RPC relative to neurogenic cell and vice versa.
```{r, fig.width=9, fig.height=3}
tic()
x <-  scEiaD_2020_v01 %>% 
  tbl("diff_testing") %>% 
  filter(Against  == "RPC",   
         Group == 'CellType (Predict)', 
         Base == "Neurogenic Cell") %>% 
  group_by(Base, Against, Gene) %>% 
  summarise(`mean log2FC` = mean(log2FoldChange), `mean padj` = mean(padj), `sig count` = sum(pvalue < 1e-2), `na count` = sum(is.na(log2FoldChange))) %>% 
  arrange(-`mean log2FC`) %>%   
  collect() %>% 
  filter(!is.na(`mean log2FC`))

# mutate(GENEID = str_extract(Gene, 'ENS\\w+')) %>% 
# left_join(gene_tab, by = 'GENEID') %>% 
# relocate(SYMBOL, GENEID) %>% 
# dplyr::rename(Symbol = SYMBOL, ID = GENEID) %>% 
# arrange(-`mean log2FC`)

down <- x %>% filter(`sig count` > 1) %>% arrange(`mean padj`) %>% filter(`mean log2FC` < 0) %>% head(5) %>% pull(Gene)
up <-  x %>% filter(`sig count` > 1) %>% arrange(`mean padj`) %>% filter(`mean log2FC` > 0) %>% head(5) %>% pull(Gene)
source('src/make_exp_plot.R')

@@

a <- make_exp_plot(input, scEiaD_2020_v01, meta_filter)

input$exp_plot_genes <- up
b <- make_exp_plot(input, scEiaD_2020_v01, meta_filter)
a_legend <- get_legend(a)
plot_grid(plot_grid(a + theme(legend.position="none"),
          b + theme(legend.position="none") + ylab(''), labels = c('a','b')),
          a_legend, ncol = 1, rel_heights = c(1,0.2))
toc()
```

```{r, fig.width=3, fig.height=7}
tic()
# flip flop diff genes
down_tab <- down_tab_big %>% 
  mutate(gene_ct_combo = paste(Symbol, Base, sep = '_')) %>% 
  filter(Base %in% ws_oct, 
         Against == 'All')

org_diff_diff_genes <- diff_tab_big %>% 
  mutate(gene_ct_combo = paste(Symbol, Base, sep = '_')) %>% 
  filter(gene_ct_combo %in% down_tab$gene_ct_combo, 
         Against == 'All') %>% 
  arrange(padj) %>% mutate(x = paste0(Symbol, ' (', ID, ')'))

genes <- scEiaD_2020_v01 %>% tbl('diff_testing_genes') %>% collect() %>% filter(grepl(org_diff_diff_genes %>% pull(ID) %>% paste0(., collapse = '|'), Gene)) %>% pull(Gene)
test <- scEiaD_2020_v01 %>%
  tbl("diff_testing") %>%
  filter(Gene %in% genes) %>%
  collect() %>%
  mutate(Symbol = str_extract(Gene, '^\\w+ ') %>% gsub(' $', '', .)) %>% 
  mutate(gene_ct_combo = paste(Symbol, Base, sep = '_')) %>% 
  filter(gene_ct_combo %in% org_diff_diff_genes$gene_ct_combo,
         Group == 'CellType (Predict)',
         Against == 'All') %>%
  select(Gene, Organism, log2FoldChange, Base)

x <- test %>% pivot_wider(values_from = log2FoldChange, names_from = Organism)
organism <- colnames(x)[c(3,4,5)]
x <- x %>% data.frame()
row.names(x) <- paste0(x$Gene,'_', x$Base)

x <- x[,-c(1,2)]

genes <- row.names(x) %>% gsub(' \\(.*','',.)

base_yo <- row.names(x) %>% gsub('.*_','',.)

hm_flipflop <- ComplexHeatmap::Heatmap(x, column_labels = organism, 
                                       row_split = base_yo, show_row_dend = FALSE, 
                                       row_labels = genes, 
                                       column_title_rot = 90, 
                                       name = 'log2FC', use_raster = TRUE,
                                       row_title_rot = 0)
hm_flipflop
toc()
```

```{r}
library(enrichR)
dbs <- c('GO_Biological_Process_2018', 'GO_Molecular_Function_2018')
enriched_cone <- enrichr(org_diff_diff_genes %>% filter(Base == 'Rod') %>% pull(Symbol), dbs)

>>>>

load('data/diff_data_pull.Rdata') # from src/diff_data_pull.R
toc()
```

@@

```{r scEiaD_data_overview, fig.height = 35, fig.width = 25, echo = F, message = F, fig.cap=scEiaD_data_overview_cap}
tic()
num1 <- meta_filter %>% filter(Organ == 'Eye') %>% pull(Tissue) %>% unique() %>% length()
num2 <- meta_filter %>% filter(Organ != 'Eye') %>% pull(Tissue) %>% unique() %>% length()
num3 <- meta_filter %>% filter(Organ == 'Eye') %>% pull(CellType) %>% unique() %>% length()
scEiaD_data_overview_cap <- fig_cap(name = 'scEiaD_data_overview', caption = glue::glue("Distribution of tissues and cell types in scEiaD. A. tabulation of the number of cells present across {num1} ocular and {num2} non-ocular tissues, B. Number of studies for each ocular tissue. C. Number of cells present across {num3} curated ocular-derived cell types."))

@@

```{r web_resources, fig.height = 15, fig.width = 20, echo = F, message = F, fig.cap=web_resources_cap}
tic()
i = 16.5 # width of the side borders in the word_document output (in centimeters)
 w = i*0.3937 # width of the side borders in the word_document output (in inches)

web_resources_cap <- tab_cap(name = 'web_resources', caption = 'Comparison of PLAE with other web resources that contain single cell ocular datasets, as of 2021-03-15.')

feature_table <- rbind(
  c('PLAE','Yes','Yes', 'Yes', '1136 ', 'https://plae.nei.nih.gov'),
  c('Spectacle', 'Yes' ,'No', 'No', '1500', 'https://singlecell-eye.org'),
  c('UCSC Cell Browser', 'Yes', 'No', 'Yes', '62', 'https://cells.ucsc.edu' ),
  c('Tabula Sapiens', 'No', 'N/A', 'Yes', '10', 'https://tabula-sapiens-portal.ds.czbiohub.org'),
  c('PanglaoDB', 'Yes', 'No', 'Yes', '47', 'https://panglaodb.se'),
  c('Protein Atlas', 'Yes*','No', 'Yes', '5',  'https://www.proteinatlas.org/humanproteome/celltype')) %>% 
  as_tibble()
colnames(feature_table) <- c('Resource Name', 'Independent Datasets', 'Harmonization', 'Ocular and non-Ocular Data', 'Ocular Cell Count\n(thousands)', 'URL')
feature_table %>% flextable() %>% width(., width = (w/(ncol(feature_table)))) 
# as of 2021 10 25
toc()
```

@@

```{r, fig.width=12}
# tic()
# # number of celltype (predict) - organism - study counts (with >=50 cells)
# # ws == Well Supported
# ws_table <- meta_filter %>%  
#   filter(Organ == 'Eye') %>% 
#   group_by(organism, CellType_predict, study_accession) %>% 
#   count() %>% 
#   filter(n >= 50) %>% 
#   ungroup() %>% 
#   group_by(organism, CellType_predict) %>% 
#   count() %>% 
#   pivot_wider(values_from = n, names_from = organism) %>% 
#   filter(!is.na(CellType_predict)) %>% 
#   replace(is.na(.), values = 0) %>% 
#   arrange(CellType_predict) %>% 
#   rename(`CellType (Predict)` = CellType_predict) %>% 
#   mutate(`Well Supported` = case_when(`Homo sapiens` >= 2 & `Mus musculus` >= 2 ~ 'Yes',
#                                       TRUE ~ 'No'))
# 
# # fix  occasional NA
# # data made from src/ensdb.R
# diff_tab_big <- read_tsv('data/diff_tab_big.tsv.gz')
# down_tab_big <- read_tsv('data/down_tab_big.tsv.gz')
# gene_tab <- bind_rows(read_tsv('data/hs.ensdb.v86.symbol.geneid.tsv.gz'), read_tsv('data/mm.ensdb.v79.symbol.geneid.tsv.gz'))
# diff_tab <- diff_tab_big %>% 
#   filter(Against == 'All', 
#          Base %in% (meta_filter %>% filter(Organ == 'Eye') %>% 
#                       pull(CellType) %>% unique()))
# 
# 
# diff_tab_sup <- diff_tab %>% 
#   group_by(Base, Organism) %>% 
#   summarise(Count = n()) %>% 
#   rename(`CellType (Predict)` = Base, `Differentially Expressed Gene Count` = Count) %>% 
#   pivot_wider(values_from = `Differentially Expressed Gene Count`, names_from = Organism) %>% replace(is.na(.),0) %>% 
#   as_tibble()
# 
# diff_tab_sup <- bind_rows(
#   diff_tab_sup,
#   ws_table$`CellType (Predict)`[!ws_table$`CellType (Predict)` %in% 
#                                   diff_tab_sup$`CellType (Predict)`] %>% 
#     enframe() %>% 
#     select(`CellType (Predict)` = value) %>%
#     mutate(`Homo sapiens` = 0, `Mus musculus` = 0, `Macaca fascicularis` = 0) %>% 
#     arrange(`CellType (Predict)`)
# )
# 
# write_csv(diff_tab, file = 'supplemental_files/differential_expression_table.csv.gz')

@@

#toc()
```

@@

```{r}
# tic()
# ws_oct <- ws_table %>% filter(`Well Supported` == 'Yes') %>% pull(`CellType (Predict)`)
# 
# consist_diff <- scEiaD_2020_v01 %>% 
#   tbl("diff_testing") %>% 
#   filter(Base %in% ws_oct) %>%  
#   filter(Group == 'CellType (Predict)', 
#          Against == 'All') %>% 
#   group_by(Base, Gene) %>% 
#   summarise(`mean log2FC` = mean(log2FoldChange), `sig count` = sum(padj < 1e-4), `mean padj` = mean(padj)) %>% 
#   filter(`mean log2FC` > 2, `sig count` > 1, `mean padj` < 1e-5) %>%  
#   collect() %>% 
#   mutate(GENEID = str_extract(Gene, 'ENS\\w+')) %>% 
#   left_join(gene_tab, by = 'GENEID') %>% 
#   relocate(SYMBOL, GENEID) %>% 
#   dplyr::rename(Symbol = SYMBOL, ID = GENEID) %>% 
#   arrange(-`mean log2FC`)
# 
# # id diff genes only seen once across the cell types
# uniq_g <- consist_diff %>% group_by(Symbol) %>% count() %>% filter(n == 1)
consist_diff %>% group_by(Base) %>% summarise(Count = n())
consist_diff %>% filter(Symbol %in% uniq_g$Symbol) %>% group_by(Base) %>% summarise(Count = n())

consist_diff %>% filter(Symbol %in% uniq_g$Symbol) %>% group_by(Base) %>% summarise(Count = n()) %>% ggplot(aes(x=`Base`, y = `Count` )) + geom_bar(stat='identity', position = 'dodge') + cowplot::theme_cowplot() + coord_flip() + xlab("CellTye (Predict)")
#toc()
```

```{r, fig.height=11, fig.width=6}
# tic()
# g <- consist_diff %>% filter(Symbol %in% uniq_g$Symbol) %>% group_by(Base) %>% slice_max(n=8, order_by = `mean log2FC`) %>% mutate(g = paste0(Symbol, ' (', ID, ')')) %>% pull(g)
# 
# consist_diff_long <- scEiaD_2020_v01 %>%
#   tbl("diff_testing") %>%
#   filter(Gene %in% g) %>%
#   collect() %>%
#   filter(Base %in% ws_oct,
#          Group == 'CellType (Predict)',
#          Against == 'All') %>%
#   select(Gene, Organism, log2FoldChange, Base)
# 
# consist_diff_wide <- consist_diff_long %>% 
#   mutate(GO = paste0(Base, '_', Organism)) %>% 
#   select(-Organism, -Base) %>% 
#   pivot_wider(values_from=log2FoldChange, names_from = GO)
# consist_diff_celltype <- colnames(consist_diff_wide[,-1])
# consist_diff_wide <- consist_diff_wide %>% data.frame()
# row.names(consist_diff_wide) <- consist_diff_wide$Gene
# 
# consist_diff_wide <- consist_diff_wide[,-1]
# 
# 
# 
# consist_diff_organism <- str_extract(consist_diff_celltype, '_\\w+ \\w+') %>% gsub('_','',.)
# consist_diff_cts  <- str_extract(consist_diff_celltype, '.*_') %>% gsub('_','',.)
# consist_diff_genes <- row.names(consist_diff_wide) %>% gsub(' \\(.*','',.)
# 
# consist_diff_base <- consist_diff_genes %>% as_tibble() %>% rename(Symbol = value) %>% left_join(consist_diff %>% select(Symbol, Base) %>% unique()) %>% pull(Base)

consist_diff_hm <- ComplexHeatmap::Heatmap(consist_diff_wide, column_labels = consist_diff_organism, 
                              column_split = consist_diff_cts, 
                              row_split = consist_diff_base, show_row_dend = FALSE, 
                              row_labels = consist_diff_genes, 
                              column_title_rot = 90, 
                              name = 'log2FC', use_raster = TRUE,
                              row_title_rot = 0)
ComplexHeatmap::draw(consist_diff_hm, padding = unit(c(2, 2, 32, 2), "mm"), row_title = "Marker Genes")
#toc()
```

@@

Neurogenic and RPC have very similar expression patterns. We leverage our more specific differential test to directly assess genes were are different between neurogenic cells and RPC. We show the top 5 genes that are both more highly expressed in RPC relative to neurogenic cell and vice versa.
```{r, fig.width=9, fig.height=3}
# tic()
# pairwise_neurogenic_test<-  scEiaD_2020_v01 %>% 
#   tbl("diff_testing") %>% 
#   filter(Against  == "RPC",   
#          Group == 'CellType (Predict)', 
#          Base == "Neurogenic Cell") %>% 
#   group_by(Base, Against, Gene) %>% 
#   summarise(`mean log2FC` = mean(log2FoldChange), `mean padj` = mean(padj), `sig count` = sum(pvalue < 1e-2), `na count` = sum(is.na(log2FoldChange))) %>% 
#   arrange(-`mean log2FC`) %>%   
#   collect() %>% 
#   filter(!is.na(`mean log2FC`))
# 
# 
# # mutate(GENEID = str_extract(Gene, 'ENS\\w+')) %>% 
# # left_join(gene_tab, by = 'GENEID') %>% 
# # relocate(SYMBOL, GENEID) %>% 
# # dplyr::rename(Symbol = SYMBOL, ID = GENEID) %>% 
# # arrange(-`mean log2FC`)
# 
# down <- pairwise_neurogenic_test %>% filter(`sig count` > 1) %>% arrange(`mean padj`) %>% filter(`mean log2FC` < 0) %>% head(5) %>% pull(Gene)
# up <-  pairwise_neurogenic_test %>% filter(`sig count` > 1) %>% arrange(`mean padj`) %>% filter(`mean log2FC` > 0) %>% head(5) %>% pull(Gene)
source('src/make_exp_plot.R')

@@

exp_plot_giga<- make_exp_plot(input, scEiaD_2020_v01, meta_filter)

input$exp_plot_genes <- up
exp_plot_iovs <- make_exp_plot(input, scEiaD_2020_v01, meta_filter)
a_legend <- get_legend(exp_plot_giga)
plot_grid(plot_grid(exp_plot_giga + theme(legend.position="none"),
          exp_plot_iovs + theme(legend.position="none") + ylab(''), labels = c('a','b')),
          a_legend, ncol = 1, rel_heights = c(1,0.2))
#toc()
```

```{r, fig.width=3, fig.height=7}
# tic()
# # flip_flop diff genes
# down_tab <- down_tab_big %>% 
#   mutate(gene_ct_combo = paste(Symbol, Base, sep = '_')) %>% 
#   filter(Base %in% ws_oct, 
#          Against == 'All')
# 
# org_diff_diff_genes <- diff_tab_big %>% 
#   mutate(gene_ct_combo = paste(Symbol, Base, sep = '_')) %>% 
#   filter(gene_ct_combo %in% down_tab$gene_ct_combo, 
#          Against == 'All') %>% 
#   arrange(padj) %>% mutate(x = paste0(Symbol, ' (', ID, ')')) 
# 
# flip_flop_genes <- scEiaD_2020_v01 %>% tbl('diff_testing_genes') %>% collect() %>% filter(grepl(org_diff_diff_genes %>% pull(ID) %>% paste0(., collapse = '|'), Gene)) %>% pull(Gene)
# flip_flop_long <- scEiaD_2020_v01 %>%
#   tbl("diff_testing") %>%
#   filter(Gene %in% genes) %>%
#   collect() %>%
#   mutate(Symbol = str_extract(Gene, '^\\w+ ') %>% gsub(' $', '', .)) %>% 
#   mutate(gene_ct_combo = paste(Symbol, Base, sep = '_')) %>% 
#   filter(gene_ct_combo %in% org_diff_diff_genes$gene_ct_combo,
#          Group == 'CellType (Predict)',
#          Against == 'All') %>%
#   select(Gene, Organism, log2FoldChange, Base)
# 
# flip_flop_wide <- flip_flop_long %>% pivot_wider(values_from = log2FoldChange, names_from = Organism)
# flip_flop_organism <- colnames(flip_flop_wide)[c(3,4,5)]
# flip_flop_wide <- flip_flop_wide %>% data.frame()
# row.names(flip_flop_wide) <- paste0(flip_flop_wide$Gene,'_', flip_flop_wide$Base)
# 
# flip_flop_wide <- flip_flop_wide[,-c(1,2)]
# 
# 
# 
# flip_flop_genes <- row.names(flip_flop_wide) %>% gsub(' \\(.*','',.)
# 
# flip_flop_base <- row.names(flip_flop_wide) %>% gsub('.*_','',.)

hm_flipflop <- ComplexHeatmap::Heatmap(flip_flop_wide, column_labels = flip_flop_organism, 
                                       row_split = flip_flop_base, show_row_dend = FALSE, 
                                       row_labels = flip_flop_genes, 
                                       column_title_rot = 90, 
                                       name = 'log2FC', use_raster = TRUE,
                                       row_title_rot = 0)
hm_flipflop
#toc()
```

```{r}
library(enrichR)
dbs <- c('GO_Biological_Process_2018', 'GO_Molecular_Function_2018')
enriched <- enrichr(org_diff_diff_genes %>% filter(Base == 'Bipolar Cell') %>% pull(Symbol), dbs)
